---
title: "streamgraphs"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_depth: 2
    toc_float: true    
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, error = F, warning = F)
```

## data

**Source**: https://files.axds.co/portals/sanctsound/plots/manifest.html by Brian Stone <brian@axiomdatascience.com>

**Files**, per [NCEI products Readme.docx](https://files.axds.co/portals/sanctsound/data/SanctSoundProducts/WCR/NCEI%20products%20Readme.docx):

- `SanctSound_CI01_01_BB_1h.csv`
  Channel Islands NMS, site 1, deployment 1, **Broadband** Sound Pressure Level, hourly
- `SanctSound_CI01_01_OL_1h.csv`
  Channel Islands NMS, site 1, deployment 1, **Octave Level**, hourly
- `SanctSound_CI01_01_PSD_1h.csv`
  Channel Islands NMS, site 1, deployment 1, **Power Spectral Density**, hourly

```{r}
library(readr)
library(dplyr)
library(tidyr)
library(purrr)
library(here)
library(DT)
# install.packages("ggplot2movies")

csvs <- list(
  bb  = here("data/SanctSound_CI01_01_BB_1h.csv"),
  ol  = here("data/SanctSound_CI01_01_OL_1h.csv"),
  psd = here("data/SanctSound_CI01_01_PSD_1h.csv"))

d <- map(csvs, read_csv)

d_smry <- tibble(
  dataset = names(d),
  cols    = map(dataset, function(x) names(d[[x]])),
  cols13  = map_chr(cols, function(x) paste(x[1:min(length(x),13)], collapse = ",")),
  dim     = map_chr(dataset, function(x) paste(dim(d[[x]]), collapse = " x ")))

d_smry %>% 
  select(dataset, dim, cols13) %>% 
  datatable()
```

### octave level

```{r}
ol <- d[["ol"]] %>% 
  rename(hour = `yyyy-mm-ddTHH:MM:SSZ`) %>% 
  select(-X13) %>% 
  pivot_longer(-hour, names_to = "octave", values_to = "level") %>% 
  mutate(
    hour_int  = as.double(hour - min(hour), units = "hours") %>%
      as.integer(),
    level_int = as.integer(level))

ol %>% 
  head(1000) %>% 
  datatable()
```

### movies example

```{r}
data(movies, package = "ggplot2movies")
movies_long <- movies  %>%
  dplyr::select(year, Action, Animation, Comedy, Drama, Documentary, Romance, Short) %>%
  tidyr::gather(genre, value, -year) %>%
  group_by(year, genre) %>%
  summarise(n = sum(value)) %>% 
  ungroup()

movies_long %>% 
  head(1000) %>% 
  datatable()
```


## `streamgraph`

- [Introduction to the streamgraph htmlwidgtet R Package](https://hrbrmstr.github.io/streamgraph/)

### movies example

```{r}
library(streamgraph)

movies_long %>%
  streamgraph("genre", "n", "year") %>%
  sg_axis_x(20, "year", "%Y") %>%
  sg_fill_brewer("PuOr") %>%
  sg_legend(show=TRUE, label="Genres: ")
```

### octave level

```{r}
ol %>% 
  streamgraph(date = "hour", value = "level_int", key = "octave") %>%
  sg_axis_x(1, "month", "%Y-%m") %>%
  sg_fill_brewer("Spectral") %>%
  #sg_fill_brewer("PuOr") %>%
  sg_legend(show=TRUE, label="Octaves: ")
```

## `highcharter`

* [Highcharter](http://jkunst.com/highcharter/)
* [Highcharts demos | Highcharts](https://www.highcharts.com/demo)

### movies example

- [dev/examples-charts/**streamgraph.R** · jbkunst/highcharter](https://github.com/jbkunst/highcharter/blob/bbd3fccecef05428e1028ac2df8e3cf46ecdc282/dev/examples-charts/streamgraph.R)

```{r}
library(highcharter)

movies_long %>% 
  hchart("streamgraph", hcaes(year, n, group = genre)) %>% 
  hc_yAxis(visible = FALSE)
```

### octave level

```{r}
ol %>% 
  hchart("streamgraph", hcaes(hour_int, level, group = octave))
```

## `plotly` - skip

* [Streamgraph with min wiggle layout | line chart made by Empet | plotly](https://plot.ly/~empet/13409.embed) nice
* [Streamgraph with ThemeRiver Layout [1] [2] | line chart made by Empet | plotly](https://plot.ly/~empet/13411/streamgraph-with-themeriver-layout-1-2.embed)
* [Streamgraph with ThemeRiver Layout [1] [2] | line chart made by Dkoffler | plotly](https://plot.ly/~dkoffler/1//#/)
  * [code](https://plot.ly/~dkoffler/1//#/code)
* issue: [Add streamgraph - Graphing Library / Plotly.py - Plotly Community Forum](https://community.plot.ly/t/add-streamgraph/12851)

  > plotly.py doesn’t have a streamgraph trace type or figure factory. To make one, you would need to compute the line locations yourself an then draw it using filled area scatter traces (https://plot.ly/python/filled-area-plots) 

